---
title: "Returning Multiple Things From a Function"
subtitle: "Most Common, Rarest, and Total Fish Caught"
author: "Ruben Sanchez Ramirez"
date: "February 22, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
```

### **Background:**

Write a function that takes a vector of fish names and always returns three items:

  + The most common fish
  + The rarest fish
  + The total number of fish
  
  **AND**
  
Include an option **(defaulted to FALSE)** that if TRUE also returns a historgram of the number of each fish type, with a title giving the total number of fish caught.

### **Function:**

The function used is referenced from the **fish_function.R** file.

The data used comes from the **fish.txt** file 

The default option is for the plot to not print.

  + This means that if no value is added other than the fish list, then the plot will not be printed
  + If the second value is set to FALSE then the plot will not print
  + If the second value is set to TRUE or an other value other than FALSE then the plot will be printed

```{r}

# Call the function from the fish_fuction R script.
source("R/fish_function.R")

# Read in the data from the .txt file
fish <- read.delim("data/fish.txt")

# Run the function for the data set
# default option is to not have the plot printed
# If "TRUE" or an other value rather then "FALSE" is entered, the plot will be printed
fish_function(fish,TRUE)

```









