---
title: "Power Required to Keep vechical at Given Speed"
subtitle: "Distribution of Power Based on Vehical and Rolling Coefficient"
author: "Ruben Sanchez Ramirez"
date: "February 22, 2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

```{r}

# setup: load packages

library(tidyverse)
library(purrr)
library(ggpubr)
library(scales)

```

### **Error Checking:**

Working from the previous Assignment 2a, we added some error checking to our function "power_watts.R"
This is a way to check for error so that if user gives garbage data, the function does not compute inaccurate power.

+ First we wanted to make sure we have the same number of mass_kg and surface_area for each car so that they are matched. This was solved by adding an "if" Statment to the function.
+ Then we wanted to make sure that the inputs for mass, surface area, and velocity were not negative. This was solved by adding "ifelse" statments for each variable.

### **Function:**

Use the same function as in Assignment2a:

**Pb = crolling * m * g * V + 1/2 A * pair * cdrag * V3**

where *crolling* and *cdrag* are rolling and aerodynamic resistive coefficients, typical values are 0.015 and 0.3, respectively

*V*: is vehicle speed (assuming no headwind) in m/s (or mps) m: is vehicle mass in kg

*A* is surface area of car (m2)

*g* is acceleration due to gravity (9.8 m/s2) pair = density of air (1.2kg/m3)

*Pb* is power in Watts

### **Effects of Highway Rolling Coefficient:**

We want to compare 4 cars with different masses and different surface areas:

* car A mass 20000 kg, area 22 m^2^

* car B mass 65000 kg, area 30 m^2^

* car C mass 38000 kg, area 22 m^2^

* car D mass 30000 kg, area 10 m^2^

**create a random sample of 100 highways each with a different rolling coefficient**
Sample the rolling coefficient from a uniform distribution with a **minimum value of 0.01 and a maximum value of 0.03**, sample 100 different highways.

### **First Use For Loops**

Other programming language (and R) use what are called loops - where repetition is more explicit

```{r}

# generate a data frame to store info on our possible cars
car_rolling = data.frame(name = c("A","B","C","D"),mass=c(20000,65000,38000,30000), area = c(22,30,22,10))

# recall our function needs speed in m/s not km/hr so we will also do a conversion
#Create conversion factor for speeds in km/hr
km_conv = 0.2778
average_speed <- 120*km_conv

# get a sample of 100 highways each with a different rolling coefficient
# sample the rolling coefficients from a uniform distribution with a min of 0.01 and a max of 0.03
rolling_coef <- runif(100, min = 0.01, max = 0.03)
summary(rolling_coef)

plot(density(rolling_coef), ylab="Distribution of Rolling Coefficients")

# in order to run all the rolling coefficients for each car we will use for loop to cycle through them
# create a data frame to store the results
# one column for each car and one row for each rolling coefficient

all_cars_loop = as.data.frame(matrix(nrow=length(rolling_coef), ncol=nrow(car_rolling)))
# because we don't initialize it - values are NA
head(all_cars_loop)

# how many cars area there
nrow(all_cars_loop)
# for loops use an index - in this case "i" but you could use anything - it repeats
# anything between the {} for each values of i between 1 and nrow(possible_car) (which is 4 in this case)

# pull function from the r scrtipt file
source("R/power_watts.R")

# index in to a matrix (like all_cars_loop) is by row and column all_cars_loop[2,5] is 2nd row and 5th column
for (i in 1:nrow(car_rolling)) {
  all_cars_loop[,i] = power_watts(
    surface_area = car_rolling$area[i], 
    mass_kg = car_rolling$mass[i], 
    velocity = average_speed, 
    rolling = rolling_coef)
}

# now it has values added
head(all_cars_loop)
# we can add column names
colnames(all_cars_loop)=car_rolling$name

# for plotting sometimes its useful to turn columns in to rows
long_loop_cars = all_cars_loop %>% pivot_longer(cols=everything(), names_to="car", values_to="power")
head(long_loop_cars)

# quick visualization
loop_plot = ggplot(long_loop_cars, aes(car,power, fill=car))+geom_boxplot() +
  scale_y_continuous(labels = comma)+
 # Add theme and titles and lables:
  theme_bw()+
  labs(title = "For Loop",
       subtitle = "Power as a Function of Rolling Coefficient",
       x = "Vehicle (Mass/Surface Area)", y = "Power in Watts")+
  scale_fill_discrete(name = "Vehicle Mass & Surface Area",
                       labels = c("A: 20,000 | 22",
                                  "B: 65,000 | 30",
                                  "C: 38,000 | 22",
                                  "D: 30,000 | 10"))+
  # Change theme variables:
  theme(text = element_text(family = "serif"),
        plot.title = element_text(size=14, face="bold"),
        plot.subtitle = element_text(size = 9, face = "bold.italic"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=10, face="bold", vjust = -1),
        axis.title.y = element_text(size=10, face="bold", vjust = 2),
        strip.text.x = element_text(size = 10, face = "bold.italic"),
        legend.title = element_text(size = 10, face = "bold.italic"),
        legend.position = "right")

# call plot
loop_plot

```

### **Second Using pmap**

*pmap* is available in the *purr* library

*mapply* is another R option

```{r}


# the first part, generating the data frame, the conversion, and rolling coefficients is the same.
# we want our samples to be the same so we will not re-run the sample for getting 100 rolling coefficients
# pmap runs a function for each value in a list of parameters, with other parameters set for each iteration

all_cars_pmap = pmap(list(surface_area = car_rolling$area, mass_kg = car_rolling$mass), 
                 power_watts, velocity = average_speed, rolling = rolling_coef)

# lets turn to a data frame for easier graphing
# we can add column names
all_cars_pmap = as.data.frame(all_cars_pmap, col.names=car_rolling$name)

head(all_cars_pmap)

# for plotting sometimes its useful to turn columns in to rows
long_pmap_cars = all_cars_pmap %>% pivot_longer(cols=everything(), names_to="car", values_to="power")
head(long_pmap_cars)

# quick visualization
pmap_plot = ggplot(long_pmap_cars, aes(car,power, fill=car))+geom_boxplot()+
   scale_y_continuous(labels = comma)+
  # Add theme and titles and lables:
  theme_bw()+
  labs(title = "PMAP",
       subtitle = "Power as a Function of Rolling Coefficient",
       x = "Vehicle (Mass/Surface Area)", y = "Power in Watts")+
  scale_fill_discrete(name = "Vehicle Mass & Surface Area",
                       labels = c("A: 20,000 | 22",
                                  "B: 65,000 | 30",
                                  "C: 38,000 | 22",
                                  "D: 30,000 | 10"))+
  # Change theme variables:
  theme(text = element_text(family = "serif"),
        plot.title = element_text(size=14, face="bold"),
        plot.subtitle = element_text(size = 9, face = "bold.italic"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=10, face="bold", vjust = -1),
        axis.title.y = element_text(size=10, face="bold", vjust = 2),
        strip.text.x = element_text(size = 10, face = "bold.italic"),
        legend.title = element_text(size = 10, face = "bold.italic"),
        legend.position = "right")

# call the plot
pmap_plot

# put plots side by side
# to confirm that they look similar
ggarrange(loop_plot, pmap_plot, common.legend = TRUE)

# compare values
head(all_cars_loop)
head(all_cars_pmap)

```







